---
title: "Introduction to StatComp21072"
author: "Weiqi Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp21072}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp21072__ is a simple R package developed for the final homework of the ‘Statistical Computing’ course in 2021 fall. Two functions are considered, namely, _semi_Robinson_ (do semiparametric linear regression using Robinson method) and _semi_Robinson_ (do semiparametric linear regression using Li method).

##semi_Robinson
The source R code for _semi_Robinson_ is as follows:
```{r,eval=FALSE}
semi_Robinson=function(y,X,Z,type=1,h,b=0.001,verbose=FALSE){
  X=as.matrix(X)
  Z=as.matrix(Z)
  
  if(type==1){
    K=function(x,h){
      return((1-abs(x/h))*(x<h)*(x>-h)/h)
    }
    print("Use Triangle kernal function")
  }
  if(type==2){
    K=function(x,h){
      return(3/4*(1-(x/h)^2)*(x<h)*(x>-h)/h)
    }
    
    print("Use Epanechnikow kernal function")
  }
  if(type==3){
    K=function(x,h){
      return(dnorm(x/h)/h)
    }
    
    print("Use Gaussian kernal function")
  }
  if(type>3){
    print("The kernal function is wrongly set, then use defult Triangle kernal function ")
  }
  
  
  n=nrow(X)
  p=ncol(X)
  q=ncol(Z)
  
  if(p>n){
    print("The demision of X is wrong")
  }
  if(q>n){
    print("The demision of Z is wrong")
  }
  
  locus1=1:q
  locus2=1:p
  locus3=1:n
  if(b>1/n){
    b=1/n
    print("The b is set unreasonable, the use the default b, which is 1/n ")
  }else{
    print("The b is set properly")
  }
  y_save=numeric(n)
  X_save=matrix(nrow=n,ncol=p)
  Z_f=numeric(n)
  
  for(i in 1:n){
    
    Z_save=sweep(Z,2,Z[i,])
    KZ=matrix(nrow=n,ncol=q)
    for(j in 1:q){
      KZ[,j]=vapply(locus3,function(i)K(Z_save[i,j],h),numeric(1))
    }
    Kh= vapply(locus3,function(j)prod(KZ[j,]),numeric(1))
    Z_f[i]=mean(Kh)
    X_median=apply(X , 2 , `*` , Kh)/Z_f[i]
    X_save[i,]=vapply(locus2,function(k)mean(X_median[,k]),numeric(1))
    y_save[i]=t(y)%*%Kh/(n*Z_f[i])
    
  }
  X_tlide=X-X_save
  y_tlide=y-y_save
  z_1=vapply(locus3,function(i)as.numeric(Z_f[i]>b),numeric(1))
  X_linear=apply(X_tlide , 2 , `*` , z_1)
  linear=lm(y_tlide~X_linear)
  beta_tlide=coef(linear)
  P_value=summary(linear)$coefficients
  
  if(verbose==FALSE){
    print("The asymptotic distribution of beta will not be computed for its complicacy")
    return(list(beta=beta_tlide,X_tlide=X_tlide,y_tlide=y_tlide,P_linear=P_value))
  }else{
    Theta=matrix(nrow = p,ncol=p)
    Phi=matrix(nrow = p,ncol=p)
    u=numeric(n)
    for(j in 1:n){
      Theta=Theta+X_tlide[i,]%*%t(X_tlide[i,])*z_1[i]
      u[i]=y_slide-t(X_slide)%*%beta_tlide
      Phi=Phi+X_tlide[i,]%*%t(X_tlide[i,])*z_1[i]*u[i]^2
    }
    Sigma=solve(Theta)%*%Phi%*%solve(Theta)
    print("The asymptotic distribution of beta is multivariate normal distribution with the mean vectors being beta_0, the covariance matrix being Sigma, which is in the list")
    return(list(beta=beta_tlide,X_tlide=X_tlide,y_tlide=y_tlide,P_linear=P_value,Sigma=Siama))
  }
}
```

##semi_Robinson
The source R code for _semi_Li_ is as follows:

```{r,eval=FALSE}
semi_Li=function(y,X,Z,type=1,h,verbose=FALSE){
  X=as.matrix(X)
  Z=as.matrix(Z)
  if(type==1){
    K=function(x,h){
      return((1-abs(x/h))*(x<h)*(x>-h)/h)
    }
    print("Use Triangle kernal function")
  }
  if(type==2){
    K=function(x,h){
      return(3/4*(1-(x/h)^2)*(x<h)*(x>-h)/h)
    }
    
    print("Use Epanechnikow kernal function")
  }
  if(type==3){
    K=function(x,h){
      return(dnorm(x/h)/h)
    }
    
    print("Use Gaussian kernal function")
  }
  if(type>3){
    print("The kernal function is wrongly set, then use defult Triangle kernal function ")
  }
  
  
  n=nrow(X)
  p=ncol(X)
  q=ncol(Z)
  
  if(p>n){
    print("The demision of X is wrong")
  }
  if(q>n){
    print("The demision of Z is wrong")
  }
  
  locus1=1:q
  locus2=1:p
  locus3=1:n
  
  y_save=numeric(n)
  X_save=matrix(nrow=n,ncol=p)
  Z_f=numeric(n)
  
  for(i in 1:n){
    
    Z_save=sweep(Z,2,Z[i,])
    KZ=matrix(nrow=n,ncol=q)
    for(j in 1:q){
      KZ[,j]=vapply(locus3,function(i)K(Z_save[i,j],h),numeric(1))
    }
    Kh= vapply(locus3,function(j)prod(KZ[j,]),numeric(1))
    Z_f[i]=mean(Kh)
    X_median=apply(X , 2 , `*` , Kh)/Z_f[i]
    X_save[i,]=vapply(locus2,function(i)mean(X_median[,i]),numeric(1))
    y_save[i]=t(y)%*%Kh/(n*Z_f[i])
    
  }
  X_tlide=X-X_save
  y_tlide=y-y_save
  
  X_linear=apply(X_tlide , 2 , `*` , Z_f)
  y_linear=y_tlide*Z_f
  linear=lm(y_linear~X_linear)
  beta_tlide=coef(linear)
  P_value=summary(linear)$coefficients
  
  if(verbose==FALSE){
    print("The asymptotic distribution of beta will not be computed for its complicacy")
    return(list(beta=beta_tlide,X_tlide=X_tlide,y_tlide=y_tlide,P_linear=P_value))
  }else{
    Theta=matrix(nrow = p,ncol=p)
    Phi=matrix(nrow = p,ncol=p)
    u=numeric(n)
    for(j in 1:n){
      Theta=Theta+X_tlide[i,]%*%t(X_tlide[i,])*(Z_f[i])^2
      u[i]=y_slide-t(X_slide)%*%beta_tlide
      Phi=Phi+X_tlide[i,]%*%t(X_tlide[i,])*(Z_f[i])^2*u[i]^2
    }
    Sigma=solve(Theta)%*%Phi%*%solve(Theta)
    print("The asymptotic distribution of beta is multivariate normal distribution with the mean vectors being beta_0, the covariance matrix being Sigma, which is in the list")
    return(list(beta=beta_tlide,X_tlide=X_tlide,y_tlide=y_tlide,P_linear=P_value,Sigma=Siama))
  }
}
```

In order to show how to use these two functions, one  downloads the red wine equality data and save it in data{StatComp}. To load the file, one simply calls _data(data)_. The R codes for using _semi_Robinson_ and _semi_Li_ are as follows.
```{r,eval=FALSE}
set.seed(123)
y1=rnorm(30)
set.seed(1)
X1=matrix(rnorm(60),nrow=30,ncol=2)
set.seed(2)
Z1=matrix(rnorm(60),nrow=30,ncol=2)
semi_Li(y=y1,X=X1,Z=Z1,h=1)
semi_Robinson(y=y1,X=X1,Z=Z1,h=1)

```





